Data_visualization

### 2018-05-15 Rmd/Data_visualization.Rmd
rmd

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)
library(forcats)
library(Hmisc)
library(Formula)

>>>>

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)
library(Hmisc)
library(Formula)
